The Astropy Project

### 2017-12-11 registry.tex
run affiliated.py: hey, it works!

\href{https://github.com/pyspeckit/pyspeckit}{pyspeckit} & Yes & \href{https://pypi.python.org/pypi/pyspeckit}{pyspeckit} & Adam Ginsburg &  \\

>>>>

\href{https://github.com/pyspeckit/pyspeckit}{pyspeckit} & Yes & \href{https://pypi.python.org/pypi/pyspeckit}{pyspeckit} & Adam Ginsburg & \citealt{pyspeckit} \\
